Cost- and Deadline-constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds

### 2012-01-10 paper/paper.tex
Add outline of algorithm
added DPDS pseudocode

\numberofauthors{2}
\author{
    \alignauthor Maciej Malawski and Jarek Nabrzyski\\
       \affaddr{University of Notre Dame}\\
       \affaddr{111 Information Technology Center}\\
       \affaddr{Notre Dame, IN, USA}\\
       \email{\{mmalawsk,naber\}@nd.edu}
    \alignauthor Gideon Juve and Ewa Deelman\\
       \affaddr{USC Information Sciences Institute}\\
       \affaddr{4676 Admiralty Way}\\
       \affaddr{Marina del Rey, CA, USA}\\
       \email{\{gideon,deelman\}@isi.edu}
}

@@

@@

\section{Algorithms}
\subsection{Dynamic Provisioning Dynamic Scheduling (DPDS)}
\subsection{Workflow-Aware DPDS (WA-DPDS)}
\subsection{Static Provisioning Static Scheduling (SPSS)}

% This is an example of how we can do algorithms
\begin{algorithm}
\caption{Euclid's algorithm}
\label{alg:euclid}
\begin{algorithmic}[1]
\Procedure{Euclid}{$a,b$}       \Comment{The g.c.d. of a and b}
    \State $r\gets a\bmod b$
    \While{$r\not=0$}           \Comment{We have the answer if r is 0}
        \State $a\gets b$
        \State $b\gets r$
        \State $r\gets a\bmod b$
    \EndWhile
    \State \textbf{return} $b$  \Comment{The gcd is b}
\EndProcedure
\end{algorithmic} 
\end{algorithm}

@@

>>>>

\numberofauthors{2}
\author{
    \alignauthor Maciej Malawski and Jarek Nabrzyski\\
       \affaddr{University of Notre Dame}\\
       \affaddr{Center for Research Computing}\\
       \affaddr{111 Information Technology Center}\\
       \affaddr{Notre Dame, IN, USA}\\
       \email{\{mmalawsk,naber\}@nd.edu}
    \alignauthor Gideon Juve and Ewa Deelman\\
       \affaddr{USC Information Sciences Institute}\\
       \affaddr{4676 Admiralty Way}\\
       \affaddr{Marina del Rey, CA, USA}\\
       \email{\{gideon,deelman\}@isi.edu}
}

@@

Workflows are important but workflow ensembles are more important, see
CyberShake or other examples.

Clouds are interesting and different from grids.

Define problems: scheduling and provisioning.

@@

\section{Algorithms}
\subsection{Dynamic Provisioning Dynamic Scheduling (DPDS)}

% This is an example of how we can do algorithms
\begin{algorithm}
\caption{Priority-based scheduling}
\label{alg:ds}
\begin{algorithmic}[1]
\Procedure{schedule}{}
    \State $Q\gets set\ of\ released\ tasks$
    \State $P\gets empty\ priority\ queue$
    \While{$Q \neq \emptyset$}
    	\For{$task\ t\in Q$}
    		\State \Call{Insert}{$t,P$} 
    	\EndFor
    	\While{$FreeVMs \neq \emptyset \wedge P \neq \emptyset $}
    		\State $VM\gets$ \Call{SelectRandom}{$FreeVMs$}
    		\State $t\gets$ \Call{Pop}{$P$}
    		\State \Call{Submit}{$t,VM$}
    	\EndWhile
    	\State \Call{Wait}{$task\ finished$}
    	\State \Call{Update}{$Q$}
    \EndWhile
\EndProcedure
\end{algorithmic} 
\end{algorithm}

\subsection{Workflow-Aware DPDS (WA-DPDS)}
\subsection{Static Provisioning Static Scheduling (SPSS)}

% This is an example of how we can do algorithms
\begin{algorithm}
\caption{Admit DAGs}
\label{alg:admit}
\begin{algorithmic}[1]
\Procedure{AdmitDAGs}{$W,b,d$}
    \State $P\gets empty\ plan$
    \State $A\gets \emptyset$ \Comment{Set of admitted DAGs}
    \For{$w\ in\ W$}
        \State $P^\prime \gets$\ \Call{PlanDAG}{$w,P,d$}
        \If{$P^\prime\ is\ a\ valid\ plan$}
            \If{$Cost(P^\prime) \le b$}
                \State $P\gets\ P^\prime$ \Comment{Accept new plan}
                \State $A \gets A\ +\ w$ \Comment{Admit w}
            \EndIf
        \EndIf
    \EndFor
    \State \textbf{return} $P,A$
\EndProcedure
\end{algorithmic} 
\end{algorithm}

\begin{algorithm}
\caption{PlanDAG}
\label{alg:plandag}
\begin{algorithmic}[1]
\Procedure{PlanDAG}{$w,P,d$}
    \State $P^\prime\gets \emptyset$
    \State assign each task in w to its cheapest resource type
    \State $cp \gets\ CriticalPath(w)$
    \While{$cp > d$}
        \State upgrade resource type of task with greatest improvement in runtime for least cost
        \State $cp \gets\ CriticalPath(w)$
    \EndWhile
    \State \Call{DeadlineDistribution}{w,d}
    \For{$t\ in\ w\ sorted\ by\ Deadline(t)$}
        \State choose resource r in $P^\prime$ that minimizes Cost(t)
        \If{$AFT(t,r) < Deadline(t)$}
            \State Schedule(t,r)
        \Else
            \State provision a new resource r
            \State Schedule(t,r)
        \EndIf
    \EndFor
    \State \textbf{return} $P^\prime$
\EndProcedure
\end{algorithmic} 
\end{algorithm}

\begin{algorithm}
\caption{Deadline Distribution}
\label{alg:deadlinedistribution}
\begin{algorithmic}[1]
\Procedure{DeadlineDistribution}{$w,d$}
    \State assign $Level(t)$ to each task t in w
    \For{$level\ l\ in\ w$}
        \State $Tasks(l) \gets$ number of tasks in l
        \State $Runtime(l) \gets$ runtime of tasks in l
    \EndFor
    \State $T \gets$ total number of tasks in w
    \State $R \gets$ total runtime of tasks in w
    \State $CP \gets$ critical path of w
    \For{$level\ l\ in\ w$}
        \State $r \gets \alpha * (Runtime(l)/R)$
        \State $t \gets (1-\alpha) * (Tasks(l)/T)$
        \State $FT(l) \gets (r + t) * (d - CP)$
    \EndFor
    \For{$task\ t\ in\ w$}
        \State $est \gets 0$
        \For{p in Pred(t)}
            \State $est \gets Deadline(p)$
        \EndFor
        \State $Deadline(t) \gets est + RT(t) + FT(Level(t))$
    \EndFor
\EndProcedure
\end{algorithmic} 
\end{algorithm}

@@

\subsection{Simulator}

\subsection{Scenarios}

\subsection{Results}
